Command line programs from LatticeRepLib

### 2023-01-12 ProgramSummary/ProgramSummary..tex
Changed the data for CmdPath to match the current code. The earlier code  was to do PointDistanceFolloer type options, which are not needed. THis program needs more work.

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	?	& ?			&\hrulefill	& Clearly not working the way it should		\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,

>>>>

		\begin{longtable}{l l l p{.2\textwidth} p{.5\textwidth} l}
			\caption{Summary of programs manipulating data}
			\label{processingprogs}\\ %NOTE: that lineskip is necessary to prevent toprule from crashing
			\toprule
			Name		&	in	&	out		&	\begin{parbox}[t]{2cm}{
				command line\\
				param{s}}
			\end{parbox}	& Output	\\
			\midrule
			CmdCmplx	&	NA	&	y		&\hrulefill	&Currently, 
				this just outputs some programmed examples.		\\[.9pt]
			CmdDelone	&	y	&	\SVI{}	&\hrulefill	&Converts input to \SVI{}		\\[.9pt]
			CmdGen		&	NA	&	\GVI{}	&	ngen - number of examples to generate (optional)\\
				{}		&		&			&type		& - lattice type to 
				generate, many options (optional) 
				c,t,h,o,r,h,m,a, 
				cP, cF,cI, tP, tI, hP, hR, oP, oF, oI, oS, mP, mC, mS, aP, 
				numeric Niggli types - 1-44, 
				Delone types - C1,C3,C5,~\dots 
				If no parameters are present, one each of the 44 Niggli types. 
				If only a number is present, that is how many of each of the 44 Niggli types to generate.
				For usage examples, see Table \ref{CMDGENexamples}\\[.9pt]
			CmdLM		&	y	&	y		&	\hrulefill		&		Lattice Matching. 
				The first input cell is used as the reference. 
				Succeeding cells are matched 
				as well as possible to the reference cell.\\[.9pt]
			CmdNiggli	&	y	&	\GVI{}	&\hrulefill	&		
				Produces the Niggli reduced cell for 	each input\\[.9pt]
			CmdPath		&	y	& \SVI{}			&
			no. of points	& If the number of points is 
			not used on the command line, the default number to generate is 20.		\\[.9pt]
			CmdPerturb	&	y	& y			&	n-number of perturbations,
